\cvsection{Work Experience}

\cvevent{Mid Backend Developer}{GuestReady / RentalReady}{Oct 2024 – Present}{Remote}
\begin{itemize}
    \item Worked on a \textbf{Property Management Software (PMS)} used by thousands of properties built on \textbf{Django}, as part of a team of over 40 developers; contributed primarily to the \textbf{backend}, with occasional contributions to the \textbf{frontend} as well.
    \item Built and maintained features integrating with third-party \textbf{APIs} like \textbf{Booking.com}, \textbf{Airbnb}, and \textbf{Vrbo}.
    \item Owned core backend components; improved \textbf{performance}, \textbf{readability}, and \textbf{maintainability} through refactoring.
    \item Investigated and resolved user-reported bugs, boosting system reliability and satisfaction.
    \item Diagnosed production issues using \textbf{Sentry} and \textbf{Datadog}.
    \item Performed bulk updates on \textbf{PostgreSQL} production databases with minimal downtime.
    \item Led and participated in \textbf{code reviews}, promoting best practices and collaboration.
\end{itemize}

\cvevent{Software Engineer}{Wavecom}{Jan 2021 – Oct 2024}{Aveiro, Portugal (Hybrid)}
\begin{itemize}
    \item Developed features in close collaboration with clients and stakeholders.
    \item Built microservices in \textbf{Python} and \textbf{Golang}; used \textbf{gRPC} and \textbf{Protocol Buffers} for service communication.
    \item Designed \textbf{REST APIs} for \textbf{SQL} and \textbf{NoSQL} databases.
    \item Containerized services with \textbf{Docker}; managed deployments via \textbf{Docker Compose}.
    \item Optimized queries for faster dashboard loading in \textbf{Grafana}.
    \item Created \textbf{ETL pipelines} with \textbf{Telegraf}; performed data analysis using \textbf{Pandas}.
    \item Developed a monitoring framework for \textbf{High-Performance Computing (HPC)} with \textbf{Grafana}, \textbf{VictoriaMetrics}, and \textbf{Python}.
    \item Automated tasks with \textbf{Makefiles} and \textbf{Bash}.
    \item Researched new technologies and built Proofs of Concept (\textbf{PoCs}).
\end{itemize}
